Approximate Code: A Cost-Effective Erasure Code for Video Applications in Cloud Storage Systems

### 2019-04-10 ApproximateCode.tex
version 3.0.1

\begin{abstract}
Multimedia data generated by autonomous driving, media industry and security monitoring is often stored in cloud storage systems and occupies a large amount of space. Meanwhile, to ensure the data reliability, distributed file systems usually use erasure code redundant data. However, the commonly used triple disk failure tolerant arrays (3DFTS) erasure code scheme is expensive not only because simultaneous damage of multiple disks is relatively rare, but also due to its ignorance of redundant information inside the data, resulting in multiple complete parity disks being excessive. On the other hand, the recently proposed approximate storage scheme can effectively reduce storage costs, but at the cost of sacrificing the reliability of some data.

In this article, we propose Approximate Code for multimedia applications, which is an erasure code using an approximation strategy. Approximate Code aims to ensure different reliability of important and minor data by means of erasure coding, thereby reducing storage overhead. It provides complete recovery when fewer disks fail, and ensures approximate recovery (recover most data) in the event of multiple disk failures. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop and Alibaba Cloud systems. The results show that compared with the typical high-reliability erasure code schemes, Approximate Code reduces the storage overhead by 7.64\% at the expense of reasonable probability of data quality loss.

@@

Therefore, we propose Approximate Codes for multimedia data that reduce storage overhead by reducing the parity of data that is not sensitive to errors. In the scenario shown in Figure \ref{apcode-72522}, the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding.
Other $s \times t$ sectors are encoded for important data thus raise its reliability. Approximate Codes ensure that the important data can tolerate $m+s$ device failures while all data can tolerate $m$ device failures.
When more than $s$ disks fails, Approximate Code recovers the important data and then transfer the surviving data to the upper layer for recovery. With proper data distribution and algorithm design, the quality loss of video or image can be controlled within an acceptable range of applications, which leads to another important task in approximating storage that is distinguishing data importance.

This work is usually done by experienced programmers, but fortunately, multimedia data is commonly compressed and stored in encoded formats, which results in a certain portion of such data being inherently more important than others. For example, in the progressive transform codec (PTC) compressed image, control and run-length bits are much more important than refinement bits. Therefore, this work is done automatically by a system tailored to specific encodings in our design.

Our work contributions include:
\begin{enumerate}
\item We propose an approximation code that reduces storage overhead and improves the reliability and availability of important data with an approximate strategy.
\item We prove the mathematical correctness of the approximation code.
\item A series of experiments show that the approximate code performs better than the traditional method in the full recovery mode, and the data loss in the approximate mode is acceptable.
\end{enumerate}

The rest of the paper is organized as follows. In Section \ref{RelatedWork}, we introduce related work and our motivation. In Section \ref{ApCode}, the design of Approximate Code and its encoding and decoding process will be illustrated in detail. The evaluation is presented in Section \ref{Evaluation} and the conclusion of our work is in Section \ref{Conclusion}.

@@

\section{Implementation}

>>>>

\begin{abstract}
Multimedia data generated by autonomous driving, media industry and security monitoring is often stored in cloud storage systems and occupies a large amount of space. Meanwhile, to ensure the data reliability, distributed file systems often use erasure codes to backup data. However, the commonly used triple disk failure tolerant arrays (3DFTS) erasure code scheme is expensive, not only because simultaneous damage of multiple disks is relatively rare, but also due to its ignorance of redundant information inside the data, resulting in multiple complete parity disks being excessive. On the other hand, the recently proposed approximate storage scheme can effectively reduce storage costs, but at the cost of sacrificing the reliability of some data.

In this article, we propose Approximate Code for multimedia applications, which is an erasure code using an approximation strategy. Approximate Code aims to ensure different reliability of important and minor data by means of erasure coding, thereby reducing storage overhead. It provides complete recovery when fewer disks fail, and ensures approximate recovery (recover most data) in the event of multiple disk failures. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop and Alibaba Cloud systems. 
\textcolor{blue}{The results show that compared with the typical high-reliability erasure code schemes, Approximate Code significantly reduces reduce the storage overhead and provide higher reliability of important data.}

@@

//////////////////////

Therefore, we propose Approximate Codes for multimedia data that reduce storage overhead by reducing the parity of data that is not sensitive to errors. In the scenario shown in Figure \ref{apcode-72522}, the Approximate Codes are designed for systems composed of $n$ disks where $m$ disks are dedicated to coding.
Other $s \times t$ sectors are encoded for important data thus raise its reliability. Approximate Codes ensure that the important data can tolerate $m+s$ device failures while all data can tolerate $m$ device failures.
When more than $s$ disks fails, Approximate Code recovers the important data and then transfer the surviving data to the upper layer for recovery.

//////////////////////

With proper data distribution and algorithm design, the quality loss of video or image can be controlled within an acceptable range of applications, which leads to another important task in approximating storage, distinguishing data importance.
This work is traditionally done by experienced programmers. Fortunately, multimedia data is commonly compressed and stored in encoded formats, which results in a certain portion of such data being more important than others. For example, in the progressive transform codec (PTC) compressed image, control and run-length bits are much more important than refinement bits. Therefore, this work can be done automatically by a system tailored to specific encodings.

Our work contributions include:
\begin{enumerate}
\item We propose Approximation Code that reduces storage overhead and improves the reliability and availability of important data with the approximate strategy.
\item We prove the mathematical correctness of the Approximation Code.
\item We perform a series of experiments and show that Approximate Code performs better than the traditional method in the full recovery mode, and the data loss in the approximate mode is acceptable.
\end{enumerate}

The rest of the paper is organized as follows. In Section \ref{RelatedWork}, we introduce related work and our motivation. 
In Section \ref{ApCode}, the design of Approximate Code and its encoding and decoding process will be illustrated in detail. 
Section \ref{Implementation} introduce the implementation of our design.
The evaluation is presented in Section \ref{evaluation} and the conclusion of our work is in Section \ref{Conclusion}.

@@

\section{Implementation}\label{Implementation}
